The title

### 2022-09-24 SIOP2023/Counts/Submission_ResourceCount.Rmd
fixed correlations (little wonky but needed to recreate `data22` object and also pull scale scores from `data22` into `data`)

# data22 <- data %>% 
# mutate_at(vars(118:372),
# function(x) recode(x,
# 1==NA, 
# 2==NA,
# 3==NA,
# 4==4,
# 5==5))

@@

data$resource <- rowSums(data[c(118:144,146:202)], na.rm=TRUE)
data$hindrance <- rowSums(data[c(203:247,249:287)], na.rm=TRUE)
data$challenge <- rowSums(data[c(288:307,309:372)], na.rm=TRUE)

data$item387 <- 7-data$item387
data$burnout      <- rowMeans(data[c(373:376)], na.rm=TRUE)
data$stress       <- rowMeans(data[c(377:379)], na.rm=TRUE)
data$engagement   <- rowMeans(data[c(380:399)], na.rm=TRUE)        ## probably need to recode some

cor(data[405:410], use="all.obs")   ## something to be told with resources and challenges

@@

r <- corx::corx(data[,c(405:410)],                    
                triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

@@

eng <- lm(engagement ~ hindrance + challenge + resource, data)
bur <- lm(burnout ~ hindrance + challenge + resource, data)
str <- lm(stress ~ hindrance + challenge + resource, data)

>>>>

 data22 <- data %>% 
 mutate_at(vars(118:372),
 function(x) recode(x,
 1==NA, 
 2==NA,
 3==NA,
 4==4,
 5==5))

@@

data22$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
data22$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
data22$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)

data22$item387 <- 7-data22$item387
data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
data22$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some

cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges

## Peculiar, but repeating for normal datafile so column identifiers line-up

data$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
data$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
data$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)

data$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
data$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
data$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some

@@

r <- corx::corx(data22[,c(405:410)],                    
                triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

@@

eng <- lm(engagement ~ hindrance + challenge + resource, data22)
bur <- lm(burnout ~ hindrance + challenge + resource, data22)
str <- lm(stress ~ hindrance + challenge + resource, data22)

### 2022-09-24 SIOP2023/Counts/Submission_ResourceCount.tex
figure heights - correlation between resource and challenge now .95 (what happened)?
fixed correlations (little wonky but needed to recreate `data22` object and also pull scale scores from `data22` into `data`)

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\begin{verbatim}
##              resource hindrance  challenge     burnout      stress engagement
## resource   1.00000000 0.4671740 0.94633436  0.07026188  0.08895664  0.3659061
## hindrance  0.46717398 1.0000000 0.46316538  0.10217550  0.14181731  0.0501684
## challenge  0.94633436 0.4631654 1.00000000  0.07838108  0.10674017  0.3358327
## burnout    0.07026188 0.1021755 0.07838108  1.00000000  0.69654076 -0.3549613
## stress     0.08895664 0.1418173 0.10674017  0.69654076  1.00000000 -0.2953456
## engagement 0.36590613 0.0501684 0.33583266 -0.35496125 -0.29534556  1.0000000
\end{verbatim}

@@

\begin{tabular}{llllllll}
\toprule
 & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
\midrule
1. resource & - &  &  &  &  & 203.85 & 56.73\\
2. hindrance & .47*** & - &  &  &  & 129.50 & 55.80\\
3. challenge & .95*** & .46*** & - &  &  & 203.12 & 57.57\\
4. burnout & .07 & .10* & .08 & - &  & 3.04 & 0.87\\
5. stress & .09* & .14*** & .11* & .70*** & - & 2.59 & 0.97\\
6. engagement & .37*** & .05 & .34*** & -.35*** & -.30*** & 4.04 & 0.83\\
\bottomrule
\end{tabular}

@@

\begin{verbatim}
## 
## Call:
## lm(formula = engagement ~ hindrance + challenge + resource, data = data)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.28900 -0.48821  0.05198  0.53450  2.07255 
## 
## Coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  3.0408396  0.1222467  24.875  < 2e-16 ***
## hindrance   -0.0022616  0.0006512  -3.473 0.000554 ***
## challenge   -0.0009931  0.0017269  -0.575 0.565461    
## resource     0.0073264  0.0017566   4.171 3.52e-05 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.763 on 564 degrees of freedom
## Multiple R-squared:  0.153,  Adjusted R-squared:  0.1485 
## F-statistic: 33.97 on 3 and 564 DF,  p-value: < 2.2e-16
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = burnout ~ hindrance + challenge + resource, data = data)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.33223 -0.67843 -0.03482  0.63254  2.10197 
## 
## Coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  2.7638017  0.1382398  19.993   <2e-16 ***
## hindrance    0.0013360  0.0007364   1.814   0.0702 .  
## challenge    0.0014508  0.0019529   0.743   0.4579    
## resource    -0.0009349  0.0019865  -0.471   0.6381    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.8628 on 564 degrees of freedom
## Multiple R-squared:  0.01206,    Adjusted R-squared:  0.006801 
## F-statistic: 2.294 on 3 and 564 DF,  p-value: 0.07694
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = stress ~ hindrance + challenge + resource, data = data)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -1.8922 -0.7552 -0.1147  0.6988  2.6438 
## 
## Coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  2.1772197  0.1541487  14.124  < 2e-16 ***
## hindrance    0.0021433  0.0008212   2.610  0.00929 ** 
## challenge    0.0032258  0.0021776   1.481  0.13907    
## resource    -0.0025593  0.0022151  -1.155  0.24842    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.9621 on 564 degrees of freedom
## Multiple R-squared:  0.02457,    Adjusted R-squared:  0.01938 
## F-statistic: 4.735 on 3 and 564 DF,  p-value: 0.00285
\end{verbatim}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\begin{verbatim}
##              resource   hindrance  challenge     burnout      stress
## resource   1.00000000 0.225550803 0.86225195  0.04841544  0.05583466
## hindrance  0.22555080 1.000000000 0.22047517  0.04101639  0.08980526
## challenge  0.86225195 0.220475168 1.00000000  0.06790884  0.08057171
## burnout    0.04841544 0.041016388 0.06790884  1.00000000  0.69654076
## stress     0.05583466 0.089805265 0.08057171  0.69654076  1.00000000
## engagement 0.34225837 0.009629535 0.31087164 -0.35496125 -0.29534556
##              engagement
## resource    0.342258369
## hindrance   0.009629535
## challenge   0.310871641
## burnout    -0.354961254
## stress     -0.295345559
## engagement  1.000000000
\end{verbatim}

@@

\begin{tabular}{llllllll}
\toprule
 & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
\midrule
1. resource & - &  &  &  &  & 36.02 & 13.26\\
2. hindrance & .23*** & - &  &  &  & 13.09 & 13.62\\
3. challenge & .86*** & .22*** & - &  &  & 35.64 & 13.63\\
4. burnout & .05 & .04 & .07 & - &  & 3.04 & 0.87\\
5. stress & .06 & .09* & .08 & .70*** & - & 2.59 & 0.97\\
6. engagement & .34*** & .01 & .31*** & -.35*** & -.30*** & 4.04 & 0.83\\
\bottomrule
\end{tabular}

@@

\begin{verbatim}
## 
## Call:
## lm(formula = engagement ~ hindrance + challenge + resource, data = data22)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.40431 -0.50713  0.02842  0.55010  2.05201 
## 
## Coefficients:
##              Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  3.276423   0.096574  33.926  < 2e-16 ***
## hindrance   -0.004436   0.002460  -1.803 0.071918 .  
## challenge    0.004175   0.004728   0.883 0.377613    
## resource     0.018672   0.004868   3.836 0.000139 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.7763 on 564 degrees of freedom
## Multiple R-squared:  0.1232, Adjusted R-squared:  0.1185 
## F-statistic: 26.41 on 3 and 564 DF,  p-value: 5.394e-16
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = burnout ~ hindrance + challenge + resource, data = data22)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.23967 -0.64759 -0.04747  0.65173  2.10310 
## 
## Coefficients:
##              Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  2.895053   0.107671  26.888   <2e-16 ***
## hindrance    0.001843   0.002743   0.672    0.502    
## challenge    0.006290   0.005271   1.193    0.233    
## resource    -0.002843   0.005427  -0.524    0.601    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.8655 on 564 degrees of freedom
## Multiple R-squared:  0.005808,   Adjusted R-squared:  0.0005199 
## F-statistic: 1.098 on 3 and 564 DF,  p-value: 0.3493
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = stress ~ hindrance + challenge + resource, data = data22)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -1.8841 -0.8038 -0.1523  0.7164  2.5693 
## 
## Coefficients:
##              Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  2.383299   0.120392  19.796   <2e-16 ***
## hindrance    0.005571   0.003067   1.816   0.0698 .  
## challenge    0.008445   0.005894   1.433   0.1525    
## resource    -0.004687   0.006068  -0.772   0.4402    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.9678 on 564 degrees of freedom
## Multiple R-squared:  0.01299,    Adjusted R-squared:  0.007741 
## F-statistic: 2.474 on 3 and 564 DF,  p-value: 0.06069
\end{verbatim}
